Tesseroids: forward modeling gravitational fields in spherical coordinates

### 2015-03-07 manuscript.tex
First try at the abstract

\begin{abstract}
\end{abstract}

>>>>

\begin{abstract}
We present the open-source software \emph{Tesseroids},
a set of command-line programs to perform the forward modeling
of gravitational fields in spherical coordinates.
The fields are calculated numerically using
the Gauss-Legendre Quadrature (GLQ).
We have improved upon an adaptive discretization algorithm
to guarantee the accuracy of the GLQ integration.
Our implementation of adaptive discretization
uses a  ``stack'' based algorithm
instead of recursion to achieve higher performance
and more control over execution errors and corner cases.
The algorithm is controlled by
a scalar called the distance-size ratio ($D$)
that determines the accuracy of the integration as well as
the computation time.
We determined optimal values of $D$
for the gravitational potential, gravitational acceleration,
and gravity gradient tensor
by comparing the computed tesseroids effects
with those of a homogeneous spherical shell.
Contrary to previous assumptions,
our results show that the potential and its first and second derivatives
require different values of $D$ to achieve a target accuracy of 0.1\%.
These values were incorporated as defaults in the software.
\end{abstract}
